--- 
title: "BrightHive Data Trust Agreement"
author:
  email: https://brighthive.io/
  name: BrightHive
date: "`r sprintf('Last updated: %s', format(Sys.time(), '%b %d, %Y at %I:%M %p'))`"
output: word_document
description: This is a preliminary draft of a reproducible Data Trust Agreement (DTA).
documentclass: book
link-citations: yes
biblio-style: apalike
params:
  eff_date:
    input: date
    label: 'Choose your effective date:'
    value: !r Sys.Date()
  members:
    input: text
    label: 'Please enter member names separated by semicolons:'
    value: Member 1; Member 2; Member 3; Member 4
  trust_name:
    input: text
    label: 'Enter the name of your Data Trust:'
    placeholder: enter name here
    value: BrightHive
  trustee:
    input: text
    label: 'Enter the name of your Technical Trustee:'
    placeholder: enter technical trustee name
    value: Technical Trustee
site: bookdown::bookdown_site
subtitle: Data Trust Legal Agreement
always_allow_html: yes
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(kableExtra)
members <- as.data.frame(str_split(params$members, ";")) %>%
  rename(`Data Trust Members` = 1) %>%
  mutate(`Data Trust Members` = as.character(`Data Trust Members`))
```

# Data Trust Agreement {-}

------
**vC0.01.16 2020**
------

## `r glue::glue('{params$trust_name} Data Trust')` {-}

This Data Trust Agreement (the "Agreement") is entered into on **`r sprintf("%s", format(params$eff_date, "%B %d, %Y"))`** ("Effective Date") by and between the members as listed in the table below ("Members"), and Technical Trustee ("Trustee"), on behalf of the `r glue::glue('{params$trust_name} Data Trust')` ("Data Trust"). Members, Data Trust, Trustee Affiliate, and Trustee may each individually be referred to herein as a "Party" and collectively as the "Parties".


```{r echo=FALSE, warning=FALSE, message=FALSE}
members %>%
   kable(format = "html", align = 'c') %>%
   kable_styling(full_width = TRUE, position = "center") %>%
   row_spec(row = 0, align = "center")
```

